Approximation as Differentiation

### 2025-03-31 notes/sec/some-categories-with-biproducts.tex
Rename.

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are the bounded lattices;
\item morphisms $f \vdash g: L \to L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in L$ and any
$y \in L'$.
\end{itemize}

>>>>

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $X, Y$ are the bounded lattices;
\item morphisms $f \vdash g: X \to Y$ are meet-semilattice homomorphisms $f: X \to Y$ paired with
join-semilattice homomorphisms $g: Y \to X$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in X$ and any
$y \in Y$.
\end{itemize}
